### 2013-07-23 Tex/chapters/appendix.tex
nu durch Mittelung bestimmt, und etwas ausführlicher beschrieben
Erweiterungen zum GG Maximum
kleine Umformulierung
\[ durch equation ersetzt

\section{Finite Size Effects at the Example of the Specific Heat}
In fig. \ref{fig:smeared_out_appendix} the specific heat
\[C = \frac{N}{T^2}\avg{\avg{E^2} - \avg{E}^2}\]
is plotted for different system sizes. The finite size effects are obvious.
The divergence is finite, and gets shallower with smaller \(L\). Besides
the maximum moves away from the critical temperature with smaller \(L\).
\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.45\textwidth]{plots/Specific_Heat_0}
    \caption[Finite Size Effects by Example of the Specific Heat]
    {
        Effects of different system sizes at \(\sigma = 0\). Dotted lines
        are guides to the eye.
    }
    \label{fig:smeared_out_appendix}
\end{figure}

>>>>

\section{Finite Size Effects at the Example of the Specific Heat}
\label{appendix:finiteSizeEffects}
    In fig. \ref{fig:smeared_out_appendix} the specific heat
    \begin{equation}
        C = \frac{N}{T^2}\avg{\avg{E^2} - \avg{E}^2}
    \end{equation}
    is plotted for different system sizes. The finite size effects are obvious.
    The divergence is finite, and gets shallower with smaller \(L\). Besides
    the maximum moves away from the critical temperature with smaller \(L\).
    \begin{figure}[htbp]
        \centering
        \includegraphics[width=0.45\textwidth]{plots/Specific_Heat_0}
        \caption[Finite Size Effects by Example of the Specific Heat]
        {
            Effects of different system sizes at \(\sigma = 0\). Dotted lines
            are guides to the eye.
        }
        \label{fig:smeared_out_appendix}
    \end{figure}

\section{Effect of $\sigma$ on the RNG}
\label{appendix:RNGDisplacement}
    todo: RNG Bilder mit versch. sigma
